### 2015-07-08 paper.tex
optimize the part: The DAQ data rate and disk storage space estimation

		The experiment hall is expected to be finished at 2019. 
		It is possible to get data from the experiment at 2020.
		The JUNO central detector's event rate is very important for 
		JUNO experiment design. So we want to estimate JUNO
		event rate by theory and Geant4 simulation. The
		JUNO event rate is composed of signal rate and background
		rate.With the estimated JUNO event rate,we can estimate the necessary
		offline disk storage space for JUNO experiment data and help the 
		online electronic and DAQ(Data Acquisition) system design.

@@

		\section{The disk storage space estimation}
		Now for the JUNO DAQ(Data Acquisition), we have several promising schemes. 
		If the electronic system can do zero suppression, we can just
		save the fired PMT's output information.
		For the normal
		events we assume the average fired PMT number is 1000, the sampling time window 
		is 1 $\mu$s. Each sampling point will occupy 2 bytes disk storage space, so each
		normal event need about 2MByes disk storage space. For the muon events, all the 
		PMTs will be fired. We assume the total PMT number of the central detector is about 
		17746, so each muon event need about 36 MBytes.

		If we can do the waveform compression, we can shorten the sampling time window from
		1 $\mu$s to 50ns. So each normal event need about 0.1MBytes disk storage space, 
		each muon event need about 1.8MBytes.

		If the electronic system can't do zero suppression, we need save all the PMT's output.
		If the sampling time window is 1 $\mu$s, each event will need 36MBytes disk storage space. 
		If we can do 
		waveform compression to shorten the sampling time window from 1 $\mu$s to 50ns, each event
		will need about 1.8MBytes.

		In the most possible DAQ scheme, we can do zero suppression in  electronic system, and can't
		do waveform compression. So for the most possible scheme we listed the estimated 
		disk storage space of central detector on different energy and radius threshold in the table.3.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The disk storage space of central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  Disk Storage Space(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m &400.598  &317.369  &315.246  &313.138  &311.188  &309.020  \\  
			R$<$11m &424.110  &319.089  &316.580  &314.189  &312.013  &309.234  \\
			R$<$12m &518.613  &325.933  &321.949  &318.466  &315.418  &310.087  \\
			R$<$13m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$14m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$15m &703.853  &347.291  &337.170  &329.547  &323.657  &312.730  \\
			R$<$16m &1049.85  &425.088  &388.524  &363.975  &347.654  &322.219  \\
			R$<$17m &1219.60  &476.504  &421.716  &385.604  &362.360  &328.461  \\

>>>>

		The experiment hall is expected to be finished at 2019. 
		It is possible to get data from the experiment at 2020.
		The JUNO central detector's event rate is very important for 
		JUNO experiment design. So we want to estimate JUNO
		event rate by theory and Geant4 simulation. The
		JUNO event rate is composed of signal rate and background
		rate.With the estimated JUNO event rate,we can estimate the necessary
		offline disk storage space for JUNO experiment data and help the 
		online electronic and DAQ system design.

@@

		\section{The DAQ data rate and disk storage space estimation}
		Now for the JUNO DAQ, we have several promising schemes. 
		If the electronic system can do zero suppression, we can just
		save the fired PMT's output information.
		For the low energy
		events we assume the average fired PMT number is 1000, the sampling time window 
		is 1 $\mu$s. Each sampling point contribute 2 bytes data, so each
		low energy event contribute 2MByes data. For the high energy muon events, all the 
		PMTs will be fired. We assume the total PMT number of the central detector is about 
		17746, so each muon event contribute 36 MBytes.

		If we can do the waveform compression, we can shorten the sampling time window from
		1 $\mu$s to 50ns. So each normal event contributes 0.1MBytes data, 
		each muon event contributes 1.8MBytes.

		If the electronic system can't do zero suppression, we need save all the PMT's output.
		If the sampling time window is 1 $\mu$s, each event contributes 36MBytes data. 
		If we can do 
		waveform compression to shorten the sampling time window from 1 $\mu$s to 50ns, each event
		contribute about 1.8MBytes.

		In the most possible DAQ scheme, we can do zero suppression in  electronic system, and can't
		do waveform compression. So for the most possible scheme we listed the estimated 
		DAQ data rate of central detector on different energy and radius threshold in the table.3.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The DAQ data rate of central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  DAQ data rate(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m &400.598  &317.369  &315.246  &313.138  &311.188  &309.020  \\  
			R$<$11m &424.110  &319.089  &316.580  &314.189  &312.013  &309.234  \\
			R$<$12m &518.613  &325.933  &321.949  &318.466  &315.418  &310.087  \\
			R$<$13m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$14m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$15m &703.853  &347.291  &337.170  &329.547  &323.657  &312.730  \\
			R$<$16m &1049.85  &425.088  &388.524  &363.975  &347.654  &322.219  \\
			R$<$17m &1219.60  &476.504  &421.716  &385.604  &362.360  &328.461  \\
